### 2023-02-18 paper.tex
Init.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor} 
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Overview Of Programming Concepts In Robotics\\}

\author{
    \IEEEauthorblockN{
        Belana Roman
    }

    \IEEEauthorblockA{
        \textit{Institute of Flight Guidance} \\
        \textit{German Aerospace Center DLR}\\
        Brunswick, Germany \\
        Belana.Roman@dlr.de
    }
    \and
    \IEEEauthorblockN{
        Noah Wiederhold
        }
    \IEEEauthorblockA{  
        \textit{In­sti­tute of Flight Sys­tems} \\
        \textit{German Aerospace Center DLR}\\
        Brunswick, Germany \\
        Noah.Wiederhold@dlr.de
    }
}

\maketitle

\begin{abstract}
    This paper gives an overview of the programming concepts in robotics. It is intended to be used as a general source of information. The paper is structured in a way that the reader get to know a number of concepts one at a time. The paper is concluded with a summary of the programming concepts in robotics.
\end{abstract}

\begin{IEEEkeywords}
    robotics, programming, concepts, ai, augmented reality, virtual reality
\end{IEEEkeywords}

\section{Introduction}

\section{Overview of Concepts}

 \begin{itemize}
    \item Online Concepts
        \begin{itemize}
            \item Playback
            \item Master-Slave
            \item Teach-in
            \item CAD/graphical based
        \end{itemize}
    \item Offline Concepts
        \begin{itemize}
            \item CAD/graphical based
            \item text based
            \item task based
                \begin{itemize}
                    \item explicit
                    \item implicit
                \end{itemize}
            \item Simulation
        \end{itemize}
    \item Hybrid Concepts
 \end{itemize}

\section{Online Concepts}

%general information about online concepts

    \subsection{Playback}
    \subsection{Master-Slave}
    \subsection{Teach-in}
    \subsection{CAD/graphical based}

\section{Offline Concepts}
    \subsection{CAD/graphical based}
    \subsection{text based}
    \subsection{task based}
        \subsubsection{explicit}
        \subsubsection{implicit}
    \subsection{Simulation}

\section{Hybrid Concepts}

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography} 
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2023-02-18 paper.tex
Added citavi

@@
 \section{Offline Concepts}
-    \subsection{CAD/graphical based}
+
     \subsection{text based}
+
+        uses problem solving programming languages 
+        gives access to commands for movements with specific parameters for the specific movement
+
+        programming enviroments for text based programming:
+            \begin{itemize}
+                \item KUKA 
+                \item ABB RobotStudio
+                \item Fanuc RobotStudio
+                \item Staubli TX
+                \item Adept
+                \item Motoman
+        (b1 p. 113)
+
     \subsection{task based}
@@
         \subsubsection{implicit}
+    \subsection{CAD/graphical based}
+
     \subsection{Simulation}
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+    \bibitem{b1} Wolfgang Weber, Heiko Koch, ''Industrieroboter Methoden der Steuerung und Regelung'' Carl Hanser Verlag München, 5. Auflage, 2022
+
 \end{thebibliography} 

### 2023-02-18 paper.tex
Grundlagen von Online-Verfahren

@@
 
+Programming with online concepts mean working with the active robot and its controls. %(TODO cite Grundlagen der Robotik Seite 186)
+This concept is used to give a robot a new set of skills in a fast and easy way, where the programmer has the chance to observe the resulting behavior directly. %(TODO cite " Seite 187)
+Commonly used concepts are Teach-in-Programming and Master-Slave-Programming.
+
 %general information about online concepts
 
-    \subsection{Playback}
+    \subsection{Teach-in}
+    With Teach-in-Programming the programmer teaches the robot needed sequences of movements.
+Therefore the programmer moves the robot via control elements or buttons, so the system can save the needed movements parameters like position, joint coordinates or the state of grippers and "learn".
+The movement of the robot can be controlled via consoles or so called "Teach Pendants", handheld programming devices.
+Usually, due to security, the movements are teached with decreased speed.
+Later on the program paramters like speed or accuracy can be adjusted to meet the needed specifications.
+Then the programm can be execute automatically, in which the robot moves through all stored positions one after the other and thus executes the planned sequence of movements.
+%(TODO cite " Seite 187-188)
+    Usually there are three forms of movements are distinguished:
+    \begin{itemize}
+        \item Point-to-Point
+        \item Continous Path
+        \item Muli-Point
+    \end{itemize}
+
+    Play-back programming is a from of Teach-in-Programming commonly used for Multi-Point.
+In this the robot is programmed by demonstrating the movement by touch or hand guidance with switched off actuators.
+Then the robot stores the positions of the joints and interpolates a smooth path with the given points, which can then be traversed as it was shown.
+%(TODO: cite " Seite 188-189)
+
     \subsection{Master-Slave}
-    \subsection{Teach-in}
-    \subsection{CAD/graphical based}
 
 \section{Offline Concepts}
-
+    \subsection{CAD/graphical based}
     \subsection{text based}
@@
                 \item Motoman
+            \end{itemize}
         (b1 p. 113)

### 2023-02-18 paper.tex
first ideas for offline concepts

@@
 
-        programming enviroments for text based programming:
-            \begin{itemize}
-                \item KUKA 
-                \item ABB RobotStudio
-                \item Fanuc RobotStudio
-                \item Staubli TX
-                \item Adept
-                \item Motoman
+        commands mostly define movements from on point to another and how to interpolate between them %source?
+
+        programming enviroments for text based from the most common robot manufacturers %quote this?
+
+        examples 
+        abb robot studio
+        uses rapid language %source?
+
+        kuka officelite
+        uses krl language %source?
+
+        in addition to the textual programming features most of the enviroments also offer a graphical programming interface
+
+        the main concepts used in these enviroments are controlling the robot by moving its arms on different axis and rotating it on those or to simulate a controller (representation of the ones used in the online concepts)
+
+        kuka mainly uses the second concept where as abb uses both
+
+        (https://new.abb.com/products/robotics/robotstudio)
+
+        some enviroments even make use of ar technologie to show the roboter and its movements in the real world 
             \end{itemize}
-        (b1 p. 113)
+
+        example robot studio
 
@@
     \subsection{CAD/graphical based}
+
+        uses a 3d scenery viewer which shows the simulated production enviroment
+
+        can simulate multiple robots and multiple tasks apart from robot movements
+
+        example visual components
+
+        (https://new.abb.com/products/robotics/robotstudio)
 

### 2023-02-19 paper.tex
added Master-Slave Online Programming

@@
 
-    Play-back programming is a from of Teach-in-Programming commonly used for Multi-Point.
+    Play-back programming is for example a special from of Teach-in-Programming commonly used for Multi-Point.
 In this the robot is programmed by demonstrating the movement by touch or hand guidance with switched off actuators.
@@
     \subsection{Master-Slave}
+    The Master-Slave-Concept gives the chance to program heavy robots via online programming wihtout having to move them manually.
+To do this, the programmer needs two coupled robots, a small one that is easy to move and the heavy robot whose capabilities are to be programmed.
+The programmer moves the small robot, the so called Master.
+These movements are then copied from the so called Slave, the heavy robot.
+Because of the need of two coupled robots, this programming concept is usually expensive and therefore only used for teleoperations, so for places humans can not visit easily like under water, irradiated areas or in space.
+%(TODO cite " Seite 190)
+
+    \subsection{Disadvantages of online programming}
+    Even though online programming makes it possible to specify motion sequences very precisely, this type of robot programming is not useful or even possible for all applications.
+This concept makes it impossible, for example, to control the program flow beyond the movements, to process sensor data or to perform mathematical calculations.
+In addition, online programming requires time, which is a great disadvantage within a manufacturing process.
+Within this time, the robot is withdrawn from the process or possibly the whole process has to be stopped for this time.
+For such problems, concepts of offline programming are used.
+%(TODO " Seite 190-191)
 
@@
         some enviroments even make use of ar technologie to show the roboter and its movements in the real world
-            \end{itemize}
 
@@
 
-\section*{Acknowledgment}
+% \section*{Acknowledgment}
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+% The preferred spelling of the word ``acknowledgment'' in America is without 
+% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+% acknowledgments in the unnumbered footnote on the first page.
 
-\section*{References}
+% \section*{References}
 
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+% Please number citations consecutively within brackets \cite{b1}. The 
+% sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+% number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+% the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
 
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
+% Number footnotes separately in superscripts. Place the actual footnote at 
+% the bottom of the column in which it was cited. Do not put footnotes in the 
+% abstract or reference list. Use letters for table footnotes.
 
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
+% Unless there are six authors or more give all authors' names; do not use 
+% ``et al.''. Papers that have not been published, even if they have been 
+% submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+% that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+% Capitalize only the first word in a paper title, except for proper nouns and 
+% element symbols.
 
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+% For papers published in translation journals, please give the English 
+% citation first, followed by the original foreign-language citation \cite{b6}.
 

### 2023-02-19 paper.tex
Added more offline concepts. Added new concepts section.

@@
 
+old-fashioned concepts
+widely used in the industry
+
  \begin{itemize}
@@
             \item task based
-                \begin{itemize}
-                    \item explicit
-                    \item implicit
-                \end{itemize}
             \item Simulation
@@
     \item Hybrid Concepts
+ \end{itemize}
+
+new or theoretical concepts
+not widely used in the industry, published in scientific papers
+
+\begin{itemize}
+    \item Semantic Robot Programming
+    %\item AI
+    %\item AR
+%\item VR
 \end{itemize}
@@
 \section{Offline Concepts}
+
+    development doesn't take place on an active robot itsself but on a seperate system, indirect programming
+    the program gets loaded onto the robot later on
+
+     (b4 p 186)
+
     \subsection{CAD/graphical based}
     \subsection{text based}
+
+        text based = explicit
+        you tell how to move to accomplish a certain task
 
@@
 
+        there are many programming languages to choose from developing using the textual concept
+        based on the 2019 market share of todays biggest robot manufacturers the most commong languages used are KAREL, RAPID, KRL
+        (s1)
+
         in addition to the textual programming features most of the enviroments also offer a graphical programming interface
@@
     \subsection{task based}
-        \subsubsection{explicit}
-        \subsubsection{implicit}
+
+        task based = implicit
+        you tell what task to do to achieve a certain goal
+        more abstract than text based, adds a layer of abstraction to the programming workflow
+
+        description of the tasks gets translated into lines of code by a task transformer (b1 p 116)
+
+        uses sensor information to add dynamic to the program while running
+
+        example task based programming enviroment:
+        RoboGuide from FANUC defining by drag and drop
+        Visual Components by flowchart
+        Robotmaster
+
     \subsection{CAD/graphical based}
@@
 
-        (https://new.abb.com/products/robotics/robotstudio)
-
     \subsection{Simulation}
@@
 \section{Hybrid Concepts}
+
+    mixing of both offline and online concepts
+    can be done by creating a general program offine and later  fine tune this programm with online concepts on the real robot
+    or the other way around by first programming the robot online and then optimizing the program offline
+    (b4 p 186)
+
+\section{New Concepts} %?
+
+    \subsection{Semantic Robot Programming}
+
+        = programming by demonstrating
+
+        in a paper ...
+the authors propose a new concept of programming robots by demonstrating the desired behavior to the robot by giving an initial state and a goal state for which the robot has to find the best way to get from the initial state to the goal state
+
+        they use a new scene estimation method called DIGEST which splits the scene into a scene graph representing the scene structure of the initial state
+        only requirement is the information about the number of objects present in the scene
+
+        given now the structure of the initial state and the goal, a task planer to find the best way to get from the initial state to the goal state is used
+
+        the task planer generates a series of actions to accomplish the task
+        (p1 p 2)
+
+    \subsection{AR}
+
+        (p3)
+
+    \subsection{VR}
+
+        (p2)
 
@@
 
-\begin{thebibliography}{00}
-    \bibitem{b1} Wolfgang Weber, Heiko Koch, ''Industrieroboter Methoden der Steuerung und Regelung'' Carl Hanser Verlag München, 5. Auflage, 2022
+\nocite{*}
 
-\end{thebibliography} 
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliographystyle{unsrt}
+\bibliography{quellen}
 
 \end{document}
+
+%maybe add the statics cited in the text?

### 2023-02-20 paper.tex
Formed sentences.

@@
 
-    development doesn't take place on an active robot itsself but on a seperate system, indirect programming
-    the program gets loaded onto the robot later on
+    Programming with offline concepts means programming the robot without the need to be in direct contact with an active robot.
+This concept is used to give a robot a new set of skills in an indirect way, without interrupting the overall production process.
+    The finished program gets loaded onto the robot afterwards, resulting in a minimum of downtime of other processes. \cite[p. 186]{b4}
 
-     (b4 p 186)
-
-    \subsection{CAD/graphical based}
     \subsection{text based}
 
-        text based = explicit
-        you tell how to move to accomplish a certain task
+        The concept of text based programming is based on the idea of programming a robot by manually writing source code in the native language of the robot or a language which can be translated into the native ones.
+The source code containing a set of instructions gets compiled like in any other programming language and the resulting program gets loaded onto the robot.
+%cite this?
+        This explicit programming approach is one of the oldest and most common programming concepts in robotics. %cite this?
 
-        uses problem solving programming languages 
-        gives access to commands for movements with specific parameters for the specific movement
+        % what are problem solving languages?
+        Most of the programming languages used in robotics are problem-solving languages, which means, that they contain special commands for certain tasks the robot can perform.
+A basic example would be a command for moving the robot from one point to another.
+This is commonly done by giving the coordinates of the initial point, a target point and arguments for how to interpolate between those points as parameter to the command.
+        The robot then calculates the path based on the parameters and moves accordingly. %cite this?
 
-        commands mostly define movements from on point to another and how to interpolate between them %source?
+        Based on the 2019 market share of today's biggest robot manufacturers the most common languages used for text based programming are RAPID, KRL and KAREL. \cite{s1}
 
-        programming enviroments for text based from the most common robot manufacturers %quote this?
+        For those languages many programming environments exist. Examples based on the mentioned would be RobotStudio from ABB, Officelite from KUKA and ROBOGUIDE from FANUC.
 
-        examples 
-        abb robot studio
-        uses rapid language %source?
+        In addition to the textual programming features most of the enviroments also offer a graphical programming interface.
+        The main concepts used in these interfaces are controlling the robot by draggable points or with a simulated controller.
+        The first method works by moving and rotating of for example the robot's arm on different axis. 
+        The second approach is based on simulated controller similar to the ones used in teach-in programming of the robot.
 
-        kuka officelite
-        uses krl language %source?
+        Some environments even make use of AR technologies to show and simulate the robot running the created program in the real world.
 
-        there are many programming languages to choose from developing using the textual concept
-        based on the 2019 market share of todays biggest robot manufacturers the most commong languages used are KAREL, RAPID, KRL
-        (s1)
-
-        in addition to the textual programming features most of the enviroments also offer a graphical programming interface
-
-        the main concepts used in these enviroments are controlling the robot by moving its arms on different axis and rotating it on those or to simulate a controller (representation of the ones used in the online concepts)
-
-        kuka mainly uses the second concept where as abb uses both
-
-        (https://new.abb.com/products/robotics/robotstudio)
-
-        some enviroments even make use of ar technologie to show the roboter and its movements in the real world
-
-        example robot studio
+        %example robot studio %cite this
 
@@
 
-        task based = implicit
-        you tell what task to do to achieve a certain goal
-        more abstract than text based, adds a layer of abstraction to the programming workflow
+        Task based programming is a more abstract and implicit approach to programming a robot.
+        Instead of describing what movement the robot should perform it defines the tasks the robot should perform.
 
-        description of the tasks gets translated into lines of code by a task transformer (b1 p 116)
+        In comparison to text based programming it adds a layer of abstraction to the programming workflow.
+For example wouldn't you have to understand the complex physic when gripping an object any more, you could just use some kind of grip command which does the task for you.
+%cite
 
-        uses sensor information to add dynamic to the program while running
+        Task based programming typically uses sensor information to add dynamic to the program while running.
+For example if the robot is supposed to pick up an object whose position is not precisely known, it would first check if the object is in the gripper and if not it would move to the object and pick it up.
+If the object is already in the gripper it would just move to the next task.
+        %cite
 
-        example task based programming enviroment:
-        RoboGuide from FANUC defining by drag and drop
-        Visual Components by flowchart
-        Robotmaster
+        Again there are many different programming environments for task based programming.
+Some examples are RoboGuide from FANUC and Visual Components.
+RoboGuide defines tasks by using a drag and drop interface, these task can later be combined to form a program.
+        Visual Components instead defines tasks by a flowchart.
+        %cite
+
+        The resulting task descriptions get translated into lines of code by a task transformer.
+These code lines then get processed like in the text based programming approach by compiling it.
+%cite this?
 
@@
 
-        uses a 3d scenery viewer which shows the simulated production enviroment
+        uses a 3d scenery viewer which shows the simulated production environment
 
@@
         example visual components
+
+        Some environments also offer to include a more mathematical approach to the programming workflow by adding different models and CAT based tools.
+        Models could range from simple models of movements to more complex simulation models of the environment and the robot itself. %TODO cite this
 

### 2023-02-20 paper.tex
added Vision-Based Programming, added advantages of online concepts

@@
 Programming with online concepts mean working with the active robot and its controls. %(TODO cite Grundlagen der Robotik Seite 186)
-This concept is used to give a robot a new set of skills in a fast and easy way, where the programmer has the chance to observe the resulting behavior directly. %(TODO cite " Seite 187)
-Commonly used concepts are Teach-in-Programming and Master-Slave-Programming.
+This concept is used to give a robot a new set of skills in a fast and easy way, where the programmer has the chance to observe the resulting behavior directly.
+Commonly used examples of online concepts are Teach-in-Programming and Master-Slave-Programming. %(TODO cite " Seite 187)
 
@@
 The movement of the robot can be controlled via consoles or so called "Teach Pendants", handheld programming devices.
+%(TODO mehr Infos zu Pendant)
         Usually, due to security, the movements are teached with decreased speed.
@@
 Because of the need of two coupled robots, this programming concept is usually expensive and therefore only used for teleoperations, so for places humans can not visit easily like under water, irradiated areas or in space.
-%(TODO cite " Seite 190)
+Since the Slave robot is usually very far away, the current scenario of the Slave is usually transmitted to the operator of the Master by camera.
+Due to transmission delays, the Slave's environment may change faster than the programmer can track it via the camera.
+This makes accurate movement corrections very difficult.
+In such cases, special algorithms are used that estimate the future positions of the Slave to make a nearly synchronous control possible.
+%(TODO cite Robotik: Programmierung intelligenter Roboter Seite 91)
+
+    \subsection{Vision-Based}
+        Another interesting concept that is not so widely used is vision-based programming.
+Here, the robot is presented with the action it should perform, which is then detected by various sensors and repeated by the robot until the action meets the expected criteria.
+%(TODO cite Handbuch Robotik Seite 178)
+        In the process, the robot must recognise and interpret the relevant features of the movement and objects it needs to interact with in the process, %(TODO cite A survey of robot programming systems)
+        which makes such a system very complex and computationally intensive. %(TODO cite Industrial robot programming by demonstration)
+
+    \subsection{Advantages of online programming}
+        A key advantage of online concepts is that no special knowledge in programming is required in order to program the necessary motion sequences into the robot.
+In addition, the robot is programmed directly in its targeted working environment, so all conditions and possible inaccuracies and disturbance variables can be taken into account directly.
+%(TODO cite Robotik: Programmierung intelligenter Roboter Seite 92)
 
@@
 For such problems, concepts of offline programming are used.
-%(TODO " Seite 190-191)
+%(TODO Grundlagen der Robotik Seite 190-191)
 

### 2023-02-22 paper.tex
Added CAD/graphical based, hybrid concepts and modern concepts

@@
 
-old-fashioned concepts
-widely used in the industry
+Widely established concepts:
 
@@
             \item task based
-            \item Simulation
         \end{itemize}
@@
 
-new or theoretical concepts
-not widely used in the industry, published in scientific papers
+Modern and theoretical concepts:
 
@@
 
-        uses a 3d scenery viewer which shows the simulated production environment
-
-        can simulate multiple robots and multiple tasks apart from robot movements
-
-        example visual components
-
-        Some environments also offer to include a more mathematical approach to the programming workflow by adding different models and CAT based tools.
+        CAD based programming environments offer a mathematical approach to the programming workflow by adding different models and CAT based tools.
         Models could range from simple models of movements to more complex simulation models of the environment and the robot itself. %TODO cite this
 
-    \subsection{Simulation}
+        %add to this?
+
+        In addition to the pure simulation of mathematical models, graphical based programming environments add a time component to the simulation, making their simulation a 4D scene.
+        They contain a kind of 3D scene viewer and offer the features to simulate not only one robot and its movements but also the whole production environment.
+This allows the user to simulate the whole production process and interactions between different parts of the production environment.
+%cite
+
+        An example for a graphical programming environment is Visual Components. %cite
 
@@
 
-    mixing of both offline and online concepts
-    can be done by creating a general program offine and later  fine tune this programm with online concepts on the real robot
-    or the other way around by first programming the robot online and then optimizing the program offline
-    (b4 p 186)
+    Hybrid concepts combine the advantages of both offline and online concepts.
+    This could for example be done by creating a general program offline and later  fine tune this program with online concepts on the real robot or the other way around by first programming the robot online and then optimizing the program offline.
+    \cite[p. 186]{b4}
 
-\section{New Concepts} %?
+\section{Modern Concepts} %?
 
@@
 
-        = programming by demonstrating
+        The concept of semantic programming is a new approach to programming robots based on demonstrating.
 
-        in a paper ...
-the authors propose a new concept of programming robots by demonstrating the desired behavior to the robot by giving an initial state and a goal state for which the robot has to find the best way to get from the initial state to the goal state
+        Recently the authors of \cite{p1} proposed a new concept of programming robots by demonstrating the desired behaviour to the robot by giving an initial state and a goal state for which the robot has to find the best way to get from the initial state to the goal state
 
-        they use a new scene estimation method called DIGEST which splits the scene into a scene graph representing the scene structure of the initial state
-        only requirement is the information about the number of objects present in the scene
-
-        given now the structure of the initial state and the goal, a task planer to find the best way to get from the initial state to the goal state is used
-
-        the task planer generates a series of actions to accomplish the task
-        (p1 p 2)
+        They used a new scene estimation method called DIGEST which splits the scene into a scene graph representing the structure of the initial state.
+The only parameter needed is the information about the number of objects present in the scene.
+The scene graph is then used to find the best way to get from the initial state to the goal state.
+        For that a task planner is used which generates a series of actions to accomplish the task. These actions are then executed by the robot. %cite this?
+        \cite[p. 2]{p1}
 
@@
 
-% \section*{Acknowledgment}
-
-% The preferred spelling of the word ``acknowledgment'' in America is without 
-% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-% acknowledgments in the unnumbered footnote on the first page.
-
-% \section*{References}
-
-% Please number citations consecutively within brackets \cite{b1}. The 
-% sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-% number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-% the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-% Number footnotes separately in superscripts. Place the actual footnote at 
-% the bottom of the column in which it was cited. Do not put footnotes in the 
-% abstract or reference list. Use letters for table footnotes.
-
-% Unless there are six authors or more give all authors' names; do not use 
-% ``et al.''. Papers that have not been published, even if they have been 
-% submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-% that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-% Capitalize only the first word in a paper title, except for proper nouns and 
-% element symbols.
-
-% For papers published in translation journals, please give the English 
-% citation first, followed by the original foreign-language citation \cite{b6}.
-
 \nocite{*}
@@
 
+\cleardoublepage
+\appendix
+
+\section{Appendix}
+    \begin{figure}[htbp!]
+        \centering
+        \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
+        \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
+        \label{fig}
+    \end{figure}
+
 \end{document}
-
-%maybe add the statics cited in the text?

### 2023-02-22 paper.tex
updated bib file and citations

@@
         \begin{itemize}
-            \item Playback
+            \item Teach-in
             \item Master-Slave
-            \item Teach-in
-            \item CAD/graphical based
+            \item Vision-Based
         \end{itemize}
@@
     \item Semantic Robot Programming
-    %\item AI
-    %\item AR
-%\item VR
+    \item AR
+    \item VR
 \end{itemize}
@@
 
-Programming with online concepts mean working with the active robot and its controls. %(TODO cite Grundlagen der Robotik Seite 186)
+Programming with online concepts mean working with the active robot and its controls. \cite[p. 186]{b4} %(Grundlagen der Robotik Seite 186)
 This concept is used to give a robot a new set of skills in a fast and easy way, where the programmer has the chance to observe the resulting behavior directly.
-Commonly used examples of online concepts are Teach-in-Programming and Master-Slave-Programming. %(TODO cite " Seite 187)
+Commonly used examples of online concepts are Teach-in-Programming and Master-Slave-Programming. \cite[p. 187]{b4}%(" Seite 187)
 
@@
 Then the programm can be execute automatically, in which the robot moves through all stored positions one after the other and thus executes the planned sequence of movements.
-%(TODO cite " Seite 187-188)
+\cite[pp.
+187-188]{b4} %(" Seite 187-188)
         Usually there are three forms of movements are distinguished:
@@
 Then the robot stores the positions of the joints and interpolates a smooth path with the given points, which can then be traversed as it was shown.
-%(TODO: cite " Seite 188-189)
+\cite[pp.
+188-189]{b4}%(" Seite 188-189)
 
@@
 In such cases, special algorithms are used that estimate the future positions of the Slave to make a nearly synchronous control possible.
-%(TODO cite Robotik: Programmierung intelligenter Roboter Seite 91)
+\cite[p.
+91]{b6}%(Robotik: Programmierung intelligenter Roboter Seite 91)
 
@@
 Here, the robot is presented with the action it should perform, which is then detected by various sensors and repeated by the robot until the action meets the expected criteria.
-%(TODO cite Handbuch Robotik Seite 178)
-        In the process, the robot must recognise and interpret the relevant features of the movement and objects it needs to interact with in the process, %(TODO cite A survey of robot programming systems)
-        which makes such a system very complex and computationally intensive. %(TODO cite Industrial robot programming by demonstration)
+\cite[p.
+178]{b5} %(Handbuch Robotik Seite 178)
+        In the process, the robot must recognise and interpret the relevant features of the movement and objects it needs to interact with in the process, \cite[p.
+7]{p4} %(A survey of robot programming systems)
+        which makes such a system very complex and computationally intensive. \cite[p. 300]{p5} %(Industrial robot programming by demonstration)
 
@@
 In addition, the robot is programmed directly in its targeted working environment, so all conditions and possible inaccuracies and disturbance variables can be taken into account directly.
-%(TODO cite Robotik: Programmierung intelligenter Roboter Seite 92)
+\cite[p.
+92]{b6} %(Robotik: Programmierung intelligenter Roboter Seite 92)
 
@@
 For such problems, concepts of offline programming are used.
-%(TODO Grundlagen der Robotik Seite 190-191)
+\cite[pp.
+190-191]{b4}%(Grundlagen der Robotik Seite 190-191)
 
@@
 \section{Appendix}
-    \begin{figure}[htbp!]
-        \centering
-        \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
-        \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
-        \label{fig}
-    \end{figure}
+    % \begin{figure}[htbp!]
+    %     \centering
+    %     \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
+    %     \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
+    %     \label{fig}
+    % \end{figure}
 

### 2023-02-22 paper.tex
Added AR and Conclusion

--- 2023-02-22 paper.tex
@@
 
-        (p3)
+        The concept of programming robots by using AR is another new approach to programming robots.
+        The general idea of AR is to integrate additional information into the real world. In our specific case this could be an overlay of the robot adding methods to control the robot.
+        The authors of \cite{p3} proposed a concept of how this could be done using a HoloLense from Microsoft.
+        For example did they add the ability to specify a pickup and a place location.
+This allows for an automatic path generation.
+The path then gets visualized in the HoloLense display.
+The user can edit this path by gestures and the movement of the robot can be simulated.
+        If the user is satisfied with the path the robot can be instructed to execute the path with a voice command. %cite this?
+        \cite[p. 2]{p3}
+
+        They found that the time needed to teach a robot using their AR based method was significantly shorter than with the traditional kinesthetic teaching approach. 
+        They also found that the average completion rate was significantly higher in a task containing movements where the path has to be made out of a high amount of distinct points, for example a sin.
+Using the AR method led to users placing more points on the path as it was easier to do so, resulting in better results in the sin movement.
+        \cite[pp. 4-5]{p3}
 
@@
         (p2)
+
+\section{Conclusion}
+
+    Generally programming robots is still a complex task and can be done in many ways. 
+    In the past the programming of robots was done by experts who had to know the complex physics of the robot and the environment.
+Modern concepts nowadays tend to simplify this task by adding abstraction layers or high level methods like AR or VR to the programming workflow.
+This allows for a more intuitive programming workflow and makes it easier for non experts to program robots.
+Modern concepts also help to reduce costs and time needed to program a robot, making the usage of robotic more accessible for small- and medium-sized companies.
+    Nevertheless, there are still many challenges to overcome before programming robots becomes a simple task for everyone.
+For example the usage of AR and VR is still limited to a few experimental environments and the usage of semantic programming is still in its infancy.
+Would these concepts improve in functionality and usability and become more widespread, they could be a big step towards a more accessible programming of robots.
 

### 2023-02-22 paper.tex
added VR

@@
     \subsection{VR}
-
-        (p2)
+        A new method of robot programming attempts to combine the advantages of online and offline concepts.
+The idea is to use Virtual Reality to define needed motion sequences offline via simulation without any effort for the programmer.
+Therefore "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} The simulation is not suitable for small changes in the motion path, which is why Online-Programming might still be needed because it allows a fine-tuning directly in the targeted manufacturing process.
+However, if further changes or updates are required, the programme can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process.
+\cite[625]{p2}
 

### 2023-02-22 paper.tex
updated VR

--- 2023-02-22 paper.tex
@@
     \subsection{VR}
-
-        (p2)
+        Another new method of robot programming attempts to combine the advantages of online and offline concepts.
+The idea is to use Virtual Reality to define needed motion sequences offline via simulation without any effort for the programmer.
+Therefore "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} For this purpose the programmer uses a VR headset which simulates a real environment and VR controllers to move freely within this simulation and to define the needed motion sequences for the robot.
+\cite[627]{p2}
+        However the simulation is not suitable for small changes in the motion path, which is why Online-Programming is still be needed.
+It allows a fine-tuning directly in the targeted manufacturing process.
+If further changes or updates are required, the programme can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process.
+\cite[625]{p2}
 
@@
 \section{Appendix}
-    % \begin{figure}[htbp!]
-    %     \centering
-    %     \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
-    %     \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
-    %     \label{fig}
-    % \end{figure}
+    \begin{figure}[htbp!]
+        \centering
+        \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
+        \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
+        \label{fig}
+    \end{figure}
 

### 2023-02-22 paper.tex
Changed abstract

@@
 The paper is structured in a way that the reader get to know a number of concepts one at a time.
-The paper is concluded with a summary of the programming concepts in robotics.
+The concepts are divided into the two categories widely established concepts and modern concepts.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-    robotics, programming, concepts, ai, augmented reality, virtual reality 
+    robotics, programming, concepts, AI, augmented reality, virtual reality 
 \end{IEEEkeywords}
@@
 
-\section{Modern Concepts} %?
+\section{Modern Concepts}
 
@@
 The scene graph is then used to find the best way to get from the initial state to the goal state.
-        For that a task planner is used which generates a series of actions to accomplish the task. These actions are then executed by the robot. %cite this?
+        For that a task planner is used which generates a series of actions to accomplish the task. These actions are then executed by the robot.
         \cite[p. 2]{p1}
@@
         The general idea of AR is to integrate additional information into the real world. In our specific case this could be an overlay of the robot adding methods to control the robot.
-        The authors of \cite{p3} proposed a concept of how this could be done using a HoloLense from Microsoft.
+        The authors of \cite{p3} proposed a concept of how this could be done using a HoloLens from Microsoft.
         For example did they add the ability to specify a pickup and a place location.
 This allows for an automatic path generation.
-The path then gets visualized in the HoloLense display.
+The path then gets visualized in the HoloLens display.
 The user can edit this path by gestures and the movement of the robot can be simulated.
-        If the user is satisfied with the path the robot can be instructed to execute the path with a voice command. %cite this?
+        If the user is satisfied with the path the robot can be instructed to execute the path with a voice command.
         \cite[p. 2]{p3}

### 2023-03-06 paper.tex
corrected spelling mistakes

@@
 
+%TODO etwas ausformulieren
 \begin{abstract}
@@
         With Teach-in-Programming the programmer teaches the robot needed sequences of movements.
-Therefore the programmer moves the robot via control elements or buttons, so the system can save the needed movements parameters like position, joint coordinates or the state of grippers and "learn".
+Therefore, the programmer moves the robot via control elements or buttons, so the system can save the needed movements parameters like position, joint coordinates or the state of grippers and "learn".
 The movement of the robot can be controlled via consoles or so called "Teach Pendants", handheld programming devices.
 %(TODO mehr Infos zu Pendant)
-        Usually, due to security, the movements are teached with decreased speed.
-Later on the program paramters like speed or accuracy can be adjusted to meet the needed specifications.
-Then the programm can be execute automatically, in which the robot moves through all stored positions one after the other and thus executes the planned sequence of movements.
+        Usually, due to security, the movements are taught with decreased speed.
+Later on the program parameters like speed or accuracy can be adjusted to meet the needed specifications.
+Then the program can be executed automatically, in which the robot moves through all stored positions one after the other and thus executes the planned sequence of movements.
 \cite[pp.
@@
             \item Point-to-Point
-            \item Continous Path
+            \item Continuous Path
             \item Muli-Point
@@
     \subsection{Master-Slave}
-        The Master-Slave-Concept gives the chance to program heavy robots via online programming wihtout having to move them manually.
+        The Master-Slave-Concept gives the chance to program heavy robots via online programming without having to move them manually.
 To do this, the programmer needs two coupled robots, a small one that is easy to move and the heavy robot whose capabilities are to be programmed.
@@
 These movements are then copied from the so called Slave, the heavy robot.
-Because of the need of two coupled robots, this programming concept is usually expensive and therefore only used for teleoperations, so for places humans can not visit easily like under water, irradiated areas or in space.
+Because of the need of two coupled robots, this programming concept is usually expensive and therefore only used for teleoperations, so for places humans can not visit easily like underwater, irradiated areas or in space.
 Since the Slave robot is usually very far away, the current scenario of the Slave is usually transmitted to the operator of the Master by camera.
@@
 178]{b5} %(Handbuch Robotik Seite 178)
-        In the process, the robot must recognise and interpret the relevant features of the movement and objects it needs to interact with in the process, \cite[p.
+        In the process, the robot must recognize and interpret the relevant features of the movement and objects it needs to interact with in the process, \cite[p.
 7]{p4} %(A survey of robot programming systems)
@@
 
-    \subsection{text based}
+    \subsection{Text based}
 
@@
 
-        In addition to the textual programming features most of the enviroments also offer a graphical programming interface.
+        In addition to the textual programming features most of the environments also offer a graphical programming interface.
         The main concepts used in these interfaces are controlling the robot by draggable points or with a simulated controller.
@@
 
-    \subsection{task based}
+    \subsection{Task based}
 
@@
         In comparison to text based programming it adds a layer of abstraction to the programming workflow.
-For example wouldn't you have to understand the complex physic when gripping an object any more, you could just use some kind of grip command which does the task for you.
+For example wouldn't you have to understand the complex physic when gripping an object anymore, you could just use some kind of grip command which does the task for you.
 %cite
@@
 
-        Again there are many different programming environments for task based programming.
+        Again there are many programming environments for task based programming.
 Some examples are RoboGuide from FANUC and Visual Components.
@@
         An example for a graphical programming environment is Visual Components. %cite
-
-\section{Hybrid Concepts}
-
-    Hybrid concepts combine the advantages of both offline and online concepts.
-    This could for example be done by creating a general program offline and later  fine tune this program with online concepts on the real robot or the other way around by first programming the robot online and then optimizing the program offline.
-    \cite[p. 186]{b4}
 
@@
 The idea is to use Virtual Reality to define needed motion sequences offline via simulation without any effort for the programmer.
-Therefore "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} For this purpose the programmer uses a VR headset which simulates a real environment and VR controllers to move freely within this simulation and to define the needed motion sequences for the robot.
+Therefore, "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} For this purpose the programmer uses a VR headset which simulates a real environment and VR controllers to move freely within this simulation and to define the needed motion sequences for the robot.
 \cite[627]{p2}
-        However the simulation is not suitable for small changes in the motion path, which is why Online-Programming is still be needed.
+        However, the simulation is not suitable for small changes in the motion path, which is why Online-Programming is still be needed.
 It allows a fine-tuning directly in the targeted manufacturing process.
-If further changes or updates are required, the programme can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process.
+If further changes or updates are required, the program can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process.
 \cite[625]{p2}
@@
         \includegraphics[scale=0.25]{./Moderne_Konzepte_Quellen/Citavi Attachments/statistic_id317178_global-industrial-robot-market-major-companies-by-market-share-2019.pdf}
-        \caption{Stastic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
+        \caption{Statistic about the market share of the biggest robot manufacturers in 2019 \cite{s1}}
         \label{fig}

### 2023-03-06 paper.tex
updated quellen.bib

@@
 
+%TODO cite b1 (Industrieroboter. Methoden der Steuerung und Regelung)
 \section{Offline Concepts}
@@
 The idea is to use Virtual Reality to define needed motion sequences offline via simulation without any effort for the programmer.
-Therefore, "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} For this purpose the programmer uses a VR headset which simulates a real environment and VR controllers to move freely within this simulation and to define the needed motion sequences for the robot.
-\cite[627]{p2}
+Therefore, "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[p.
+625]{p2} For this purpose the programmer uses a VR headset which simulates a real environment and VR controllers to move freely within this simulation and to define the needed motion sequences for the robot.
+\cite[p.
+627]{p2}
         However, the simulation is not suitable for small changes in the motion path, which is why Online-Programming is still be needed.
@@
 If further changes or updates are required, the program can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process.
-\cite[625]{p2}
+\cite[p.
+625]{p2}
 
@@
 
-\nocite{*}
-
 \bibliographystyle{unsrt}
 \bibliography{quellen}
+
+\nocite{*}
 

### 2023-03-12 paper.tex
added presentation
updated presentation

@@
 \begin{IEEEkeywords}
-    robotics, programming, concepts, AI, augmented reality, virtual reality 
+    robotics, programming, concepts, augmented reality, virtual reality 
 \end{IEEEkeywords}
@@
         \end{itemize}
-    \item Hybrid Concepts
  \end{itemize}
@@
 
-        CAD based programming environments offer a mathematical approach to the programming workflow by adding different models and CAT based tools.
+        CAD based programming environments offer a mathematical approach to the programming workflow by adding different models and CAD based tools.
         Models could range from simple models of movements to more complex simulation models of the environment and the robot itself. %TODO cite this

### 2023-03-15 paper.tex
added final citations

@@
 The movement of the robot can be controlled via consoles or so called "Teach Pendants", handheld programming devices.
-%(TODO mehr Infos zu Pendant)
 Usually, due to security, the movements are taught with decreased speed.
@@
 \cite[pp.
-187-188]{b4} %(" Seite 187-188)
+187 - 188]{b4} %(" Seite 187-188)
         Usually there are three forms of movements are distinguished:
@@
 \cite[pp.
-188-189]{b4}%(" Seite 188-189)
+188 - 189]{b4}%(" Seite 188-189)
 
@@
 \cite[pp.
-190-191]{b4}%(Grundlagen der Robotik Seite 190-191)
+190 - 191]{b4}%(Grundlagen der Robotik Seite 190-191)
 
-%TODO cite b1 (Industrieroboter. Methoden der Steuerung und Regelung)
 \section{Offline Concepts}
@@
         The concept of text based programming is based on the idea of programming a robot by manually writing source code in the native language of the robot or a language which can be translated into the native ones.
-The source code containing a set of instructions gets compiled like in any other programming language and the resulting program gets loaded onto the robot.
-%cite this?
-        This explicit programming approach is one of the oldest and most common programming concepts in robotics. %cite this?
+\cite[p.
+184]{b5}
+        The source code containing a set of instructions gets compiled or interpreted like in any other programming language and the resulting program gets loaded onto the robot. \cite[p. 197]{b4}
+        This explicit programming approach is one of the oldest and most common programming concepts in robotics. \cite[p. 105]{b6}
 
         % what are problem solving languages?
-        Most of the programming languages used in robotics are problem-solving languages, which means, that they contain special commands for certain tasks the robot can perform.
+        A lot of programming languages used in robotics are problem-solving or implicit languages, which means, that they contain special commands for certain tasks the robot can perform.
 A basic example would be a command for moving the robot from one point to another.
 This is commonly done by giving the coordinates of the initial point, a target point and arguments for how to interpolate between those points as parameter to the command.
-        The robot then calculates the path based on the parameters and moves accordingly. %cite this?
+The robot then calculates the path based on the parameters and moves accordingly.
+\cite[pp.
+186 - 187]{b5}
 
@@
 
-        For those languages many programming environments exist. Examples based on the mentioned would be RobotStudio from ABB, Officelite from KUKA and ROBOGUIDE from FANUC.
+        For those languages many programming environments exist.
+Examples based on the mentioned would be RobotStudio from ABB \cite{i1}, Officelite from KUKA \cite{i2} and ROBOGUIDE from FANUC \cite{i3}.
 
@@
         The first method works by moving and rotating of for example the robot's arm on different axis. 
-        The second approach is based on simulated controller similar to the ones used in teach-in programming of the robot.
+        The second approach is based on simulated controller similar to the ones used in teach-in programming of the robot. \cite[pp. 106 - 108]{b2}
 
-        Some environments even make use of AR technologies to show and simulate the robot running the created program in the real world.
-
-        %example robot studio %cite this
+        Some environments, like RobotStudio from ABB, even make use of AR technologies to show and simulate the robot running the created program in the real world. \cite{i4}
 
@@
 Instead of describing what movement the robot should perform it defines the tasks the robot should perform.
-
 In comparison to text based programming it adds a layer of abstraction to the programming workflow.
 For example wouldn't you have to understand the complex physic when gripping an object anymore, you could just use some kind of grip command which does the task for you.
-%cite
-
         Task based programming typically uses sensor information to add dynamic to the program while running.
@@
 If the object is already in the gripper it would just move to the next task.
-        %cite
+\cite[pp.
+114 - 115]{b1}
 
-        Again there are many programming environments for task based programming.
-Some examples are RoboGuide from FANUC and Visual Components.
-RoboGuide defines tasks by using a drag and drop interface, these task can later be combined to form a program.
-        Visual Components instead defines tasks by a flowchart.
-        %cite
+        Again there are many programming environments for task based programming. Some examples are ROBOGUIDE from FANUC \cite{i3} and Visual Components \cite{i5}.
 
@@
 These code lines then get processed like in the text based programming approach by compiling it.
-%cite this?
+\cite[p.
+115]{b1}
 
@@
         CAD based programming environments offer a mathematical approach to the programming workflow by adding different models and CAD based tools.
-        Models could range from simple models of movements to more complex simulation models of the environment and the robot itself. %TODO cite this
-
-        %add to this?
-
+        Models could range from simple models of movements to more complex simulation models of the environment and the robot itself.
         In addition to the pure simulation of mathematical models, graphical based programming environments add a time component to the simulation, making their simulation a 4D scene.
@@
 This allows the user to simulate the whole production process and interactions between different parts of the production environment.
-%cite
+\cite[pp.
+192 - 194]{b4}
 
-        An example for a graphical programming environment is Visual Components. %cite
+        The already mentioned programming environment Visual Components is an example that also offers a graphical approach in its environment. \cite{i5}
 
@@
 Using the AR method led to users placing more points on the path as it was easier to do so, resulting in better results in the sin movement.
-        \cite[pp. 4-5]{p3}
+        \cite[pp. 4 - 5]{p3}
 

### 2023-03-30 paper.tex
s
latest revision

@@
 It is intended to be used as a general source of information.
-The paper is structured in a way that the reader get to know a number of concepts one at a time.
+The paper is structured in a way that the reader gets to know a number of concepts one at a time.
 The concepts are divided into the two categories widely established concepts and modern concepts.
@@
 Usually, due to security, the movements are taught with decreased speed.
-Later on the program parameters like speed or accuracy can be adjusted to meet the needed specifications.
-Then the program can be executed automatically, in which the robot moves through all stored positions one after the other and thus executes the planned sequence of movements.
+Later on the program parameters like speed or accuracy can be adjusted to attain the needed specifications.
+Then the program can be executed automatically, in which the robot moves through all stored positions sequentially and thus executes the planned sequence of movements.
 \cite[pp.
@@
             \item Continuous Path
-            \item Muli-Point
+            \item Multi-Point
         \end{itemize}
 
-        Play-back programming is for example a special from of Teach-in-Programming commonly used for Multi-Point.
+        Play-back programming is for example a special form of Teach-in-Programming commonly used for Multi-Point.
 In this the robot is programmed by demonstrating the movement by touch or hand guidance with switched off actuators.
@@
 A basic example would be a command for moving the robot from one point to another.
-This is commonly done by giving the coordinates of the initial point, a target point and arguments for how to interpolate between those points as parameter to the command.
+This is commonly done by giving the coordinates of the initial point, a target point and arguments for interpolating between those points as parameter to the command.
 The robot then calculates the path based on the parameters and moves accordingly.
@@
 
-        Based on the 2019 market share of today's biggest robot manufacturers the most common languages used for text based programming are RAPID, KRL and KAREL. \cite{s1}
+        Based on the 2019 market share of today's biggest robot manufacturers the most common languages used for text based programming are RAPID, KRL and KAREL.
+\cite{s1} The market share can be seen in figure \ref{fig}.
 
@@
         In addition to the pure simulation of mathematical models, graphical based programming environments add a time component to the simulation, making their simulation a 4D scene.
-        They contain a kind of 3D scene viewer and offer the features to simulate not only one robot and its movements but also the whole production environment.
+        They contain a kind of 3D scene viewer and offer features to simulate not only one robot and its movements but also the whole production environment.
 This allows the user to simulate the whole production process and interactions between different parts of the production environment.
@@
 
-        They found that the time needed to teach a robot using their AR based method was significantly shorter than with the traditional kinesthetic teaching approach. 
-        They also found that the average completion rate was significantly higher in a task containing movements where the path has to be made out of a high amount of distinct points, for example a sin.
-Using the AR method led to users placing more points on the path as it was easier to do so, resulting in better results in the sin movement.
+        They found that the time needed to teach a robot using their AR based method was significantly shorter than with the traditional teaching approach. 
+        They also found that the average completion rate was significantly higher in a task containing movements where the path has to be made out of a high amount of distinct points, for example a sine.
+Using the AR method led to users placing more points on the path as it was easier to do so, resulting in better results in the sine movement.
         \cite[pp. 4 - 5]{p3}
@@
 627]{p2}
-        However, the simulation is not suitable for small changes in the motion path, which is why Online-Programming is still be needed.
+        However, the simulation is not suitable for small changes in the motion path, therefore Online-Programming is still needed.
 It allows a fine-tuning directly in the targeted manufacturing process.
